Blocking-resistant communication\\through domain fronting

### 2014-07-24 docs/meek.tex
Note to talk about Psiphon's long-polling design.
Note to add a figure.
Put GoAgent GFW disruption after Collateral Freedom survey.
Threat model revisions.

@@

GoAgent~\cite{goagent} is a direct inspiration for meek in its use of App
Engine and Host header--based domain fronting.
Traffic is fronted by the Google frontend server
and delivered to its destination by a specialized app running on App Engine.
GoAgent uses the ``domainless'' fronting model without SNI for most target domains.
GoAgent doesn't use an additional general-purpose proxy after fronting;
rather, HTTP and HTTPS URLs are fetched directly from the App Engine servers,
meaning that GoAgent is limited to carrying HTTP and HTTPS traffic,
and the contents of all communications are revealed to App Engine.
Users of GoAgent upload their own personal copy of the proxy code to App Engine,
which is free of charge as long as they do not exceed a bandwidth quota.
Use of GoAgent in China was disrupted starting in the beginning of June~2014
when all Google services (including GoAgent's front domains) were blocked.
meek over App Engine was similarly affected.
According to a May 2013 survey~\cite{collateral-freedom},
GoAgent was the circumvention tool most used in
China, with 35\% of survey respondents having used it in the previous month.
This figure is higher than that of paid~(29\%) and free VPNs~(18\%), and far
above that of other special-purpose tools like Tor~(2.9\%) and Psiphon~(2.5\%).
Users identified reliability, speed, and ease of installation as the most important features of a circumvention tool.

@@

The censor is able to inspect all traffic that passes through
the censorship boundary and block or allow it at will.
The censor is able to actively scan for proxies, and issue followup
connections to hosts that clients connect to, in order to determine
whether they are proxies.
The censor may block the web host on which the reflector web app runs,
but it must allow access to some domain that can front for it.
In our deployment using App Engine, the censor may block appspot.com,
but must allow www.google.com (or its IP address, or some other domain
that goes through the frontend server).

The censor must operate at line rate; that is,
it must not delay traffic unduly while deciding whether to allow it.
This consideration is one facet of the censor's sensitivity to
collateral damage caused by false positives:
mistakenly blocking or degrading non-circumvention traffic causes the censor
to incur some penalty, just as mistakenly allowing circumvention traffic does.
The censor must allow TLS connections; meek does not try to look like plaintext.
% but the censor may look at TLS characteristics and block suspicious connections.

The user's computer, the third-party infrastructure (e.g., Google), and the Tor bridge
are all uncontrolled and uncompromised by the censor.
The user has a way to get a copy of the necessary client programs.

We assume that the censor cannot observe the communication
once it reaches the third-party infrastructure; i.e.,
that no further obfuscation is needed once fronting is accomplished.
% What about in-country edge servers; seems to work.

@@

@@

>>>>

% We measure the performance...

@@

GoAgent~\cite{goagent} is a direct inspiration for meek in its use of App
Engine and Host header--based domain fronting.
Traffic is fronted by the Google frontend server
and delivered to its destination by a specialized app running on App Engine.
GoAgent uses the ``domainless'' fronting model without SNI for most target domains.
GoAgent doesn't use an additional general-purpose proxy after fronting;
rather, HTTP and HTTPS URLs are fetched directly from the App Engine servers,
meaning that GoAgent is limited to carrying HTTP and HTTPS traffic,
and the contents of all communications are revealed to App Engine.
Users of GoAgent upload their own personal copy of the proxy code to App Engine,
which is free of charge as long as they do not exceed a bandwidth quota.
According to a May 2013 survey~\cite{collateral-freedom},
GoAgent was the circumvention tool most used in
China, with 35\% of survey respondents having used it in the previous month.
This figure is higher than that of paid~(29\%) and free VPNs~(18\%), and far
above that of other special-purpose tools like Tor~(2.9\%) and Psiphon~(2.5\%).
Use of GoAgent in China was disrupted starting in the beginning of June~2014
when all Google services (including GoAgent's front domains) were blocked.
meek over App Engine was similarly affected.
% Users identified reliability, speed, and ease of installation as the most important features of a circumvention tool.

@@

The model includes four actors:
the censor,
the censored client,
the intermediate web service's frontend server (CDN edge server),
and the destination proxy (Tor bridge).
Circumvention is achieved when the client evades the censor to reach
the destination proxy,
because the proxy provides access to anywhere.
The client and destination proxy cooperate with each other.
The intermediate web service does not cooperate with either,
except to the extent that it doesn't collude with the censor.
% The censor's goal is to prevent circumvention.

The censor controls a network and the into and within it.
The censor is able to inspect traffic flowing across all links under its control
and may block or allow any packet.
The censor may inject and replay traffic, and
operate its own clients and servers.
The client lies within the censor's network,
while the intermediate web service and destination proxy lie outside the network.
The censor blocks direct communication between the client and the destination proxy,
but allows HTTPS between the client and at least one front domain or IP address
on the intermediate web service.

% The censor must operate at line rate; that is,
% it must not delay traffic unduly while deciding whether to allow it.
% This consideration is one facet of the censor's sensitivity to
% collateral damage caused by false positives:
% mistakenly blocking or degrading non-circumvention traffic causes the censor
% to incur some penalty, just as mistakenly allowing circumvention traffic does.

The client,
intermediate web service,
and destination proxy
are uncontrolled by the censor.
The censor does not control a TLS certificate authority;
specifically it cannot man-in-the-middle an HTTPS session
without being caught by ordinary certificate verification.
The client has a way to get a copy of the necessary client programs.

See Section~\ref{sec:security} for what happens when some
of these assumptions are violated;
specifically what happens
when the intermediate web service's frontend server is inside the censor's network
and when the censor controls a certificate authority.

% What about in-country edge servers; seems to work.

@@

% Use a child's garden--like figure of the HTTP protocol here.
% "concatenates successive bodies"

@@

% Psiphon idea: use long-polling for downstream data.
% Works with CDNs, not with App Engine.
